Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2019-02-24 documentation/report.tex
Properly explained DEAP algorithms

In DEAP-3600, the key challenge is the aforementioned unusual detector format: a sphere tiled with a hexagonal lattice of PMTs. I approached this problem in three different ways:

\begin{enumerate}
    \item I tried simply inputting photon counts from each PMT into a multi-layer perceptron.
    \item I developed and applied a Mercator-like cylindrical projection, and used a 2D CNN.
    \item I developed an entirely new type of CNN, called a topological CNN. Rather than a 2D image of square pixels, kernels convolve over an arbitrary topology.
\end{enumerate}

>>>>

In DEAP-3600, the key challenge is the aforementioned unusual detector format: a sphere (with an opening on the top) tiled with a hexagonal lattice of PMTs. I approached this problem in three different ways:

\begin{enumerate}
    \item I tried simply inputting photon counts from each PMT into a multi-layer perceptron.

    \item I developed and applied a Mercator-like cylindrical projection, by mapping each row of nodes in the sphere to a row in a rectangular image. Cubic spline interpolation was used to map latitude lines on the sphere (which vary in length) to equal-length rows on the rectangular image.

    \item I developed a new type of CNN, called a topological CNN. Rather than a 2D image of square pixels, kernels convolve over an arbitrary topology.

    While a conventional convolutional layer downscales a rectangular image to a smaller rectangular image by multiplying square regions by a set of corresponding weights, a topological CNN (as applied to this problem) downscales the approximately spherical hexagonal mesh to a smaller but topologically equivalent hexagonal mesh.
\end{enumerate}
